### 2015-09-09 Irregular-occ/Irregular-occ.tex
.

Up to date no stellar occultation by irregular satellite is found in the literature. Since their estimated sizes are very small (see table \ref{} \textcolor{red}{Ainda vou fazer a tabela}), prediction of the exact location and instant where the shadow will cross the Earth demands a good accurate ephemeris and star positions. For instance, Himalia, supposedly the largest irregular satellite of Jupiter has an estimated size of 150 km \citep{Porco2003}, which is equivalent to an apparent size of about 40 mas (milliarcseconds).Thus, even in the best cases, the overall budget of ephemeris and star position errors must be around 40 mas in order that we get good chances of observing a stellar occultation.

@@

The prediction of the occultations was made by crossing the stellar coordinates and proper motions of the UCAC4 catalogue \citep{Zacharias2013} with the corrected JPL ephemeris as presented in section \ref{Sec: Offset}. The search for stellar candidates follows the same procedure as presented by \cite{Assafin2010, Assafin2012} and \cite{Camargo2013}.

We predicted occultation for the 7 major irregular satellites of Jupiter, Phoebe of Saturn and Triton and Nereid of Neptune.

For Triton and Nereid, the candidates for stellar occultations in 2015 and 2016 was searched using the WFI catalogue in the same way as the predictions for Centaurs and TNOs occultations by \cite{Assafin2010, Assafin2012} and \cite{Camargo2013}. This catalogue contains the stars in the path of Neptune in the sky up to mid-2016. The catalogue was generated by observations made at the ESO 2p2 telescope (IAU code 809) using the Wide Field Imager (WFI) CCD mosaic detector. The filter used was the broad-band R filter ESO\#844 with $\lambda_c$ = 651.725 nm and $\Delta\lambda$ = 162.184 nm.

@@

\section{Conclusion} \label{Sec: conclusions}

>>>>

Up to date no stellar occultation by irregular satellite is found in the literature. Since their estimated sizes are very small (see table \ref{Tab: satellite-diameter}), prediction of the exact location and instant where the shadow will cross the Earth demands a good accurate ephemeris and star positions. For instance, Himalia, supposedly the largest irregular satellite of Jupiter has an estimated size of 150 km \citep{Porco2003}, which is equivalent to an apparent size of about 40 mas (milliarcseconds).Thus, even in the best cases, the overall budget of ephemeris and star position errors must be around 40 mas in order that we get good chances of observing a stellar occultation.

\begin{table}
\caption{\label{Tab: satellite-diameter} Estimated diameter of the satellites and correspondent apparent diameter}
\begin{centering}
\begin{tabular}{lccc}
\hline  \hline
\multicolumn{4}{c}{Diameter of the satellites} \tabularnewline
Satellite  & km  & mas\tablefootmark{a} & References \tabularnewline
\hline
Ananke & 29 &  & 1 \tabularnewline
Carme & 46 &  & 1 \tabularnewline
Elara & 86 &  & 1 \tabularnewline
Himalia & $(150 \pm 20) \times (120\pm 20)$ &  & 2 \tabularnewline
Lysithea & 36 &  & 1 \tabularnewline
Pasiphae & 62 & & 1 \tabularnewline
Sinope & 37 & & 1 \tabularnewline
\hdashline
Phoebe & $212 \pm 1.4$ & & 3 \tabularnewline
\hdashline
Nereid & $340 \pm 50$ &  & 4 \tabularnewline
Triton & $2707 \pm 2.0$ &  & 5 \tabularnewline
\hline
\end{tabular}
\tablebib{
(1) \cite{Rettig2001}; (2) \cite{Porco2003}; (3) \cite{Thomas2010}; (4) \cite{Thomas1991} (5) \cite{Thomas2000}.}
\end{centering}
\tablefoottext{a}{Using a mean distance from Jupiter of XX AU, from Saturn of XX AU and from Neptune of XX AU.}
\par
\end{table}

@@

The prediction of the occultations was made by crossing the stellar coordinates and proper motions of the UCAC4 catalogue \citep{Zacharias2013} with the corrected JPL ephemeris as presented in section \ref{Sec: Offset}. The search for stellar candidates follows the same procedure as presented by \cite{Assafin2010, Assafin2012} and \cite{Camargo2014}.

We predicted occultation for the 7 major irregular satellites of Jupiter:  Ananke, Carme, Elara, Himalia, Lysithea, Pasiphae, and Sinope; Phoebe of Saturn and Triton and Nereid of Neptune.

For Triton and Nereid, the candidates for stellar occultations in 2015 and 2016 was searched using the WFI catalogue in the same way as the predictions for Centaurs and TNOs occultations by \cite{Assafin2010, Assafin2012} and \cite{Camargo2014}. This catalogue contains the stars in the path of Neptune in the sky up to mid-2016. The catalogue was generated by observations made at the ESO 2p2 telescope (IAU code 809) using the Wide Field Imager (WFI) CCD mosaic detector. The filter used was the broad-band R filter ESO\#844 with $\lambda_c$ = 651.725 nm and $\Delta\lambda$ = 162.184 nm.

@@

\section{Discussion} \label{Sec: conclusions}

We presented stellar occultations for the period of 2015-2017 for seven irregular satellites of Jupiter: Ananke, Carme, Elara, Himalia, Lysithea, Pasiphae, and Sinope; one satellite of Saturn: Phoebe; and two satellites of Neptune: Triton and Nereid. The procedure used was the same that predicted stellar occultations by Pluto and its satellites in \cite{Assafin2010} and by Centaurs and TNOs in \cite{Assafin2012} and \cite{Camargo2014}.

The candidate stars was searched in the UCAC4 catalogue, except for the candidates in 2015 and 2016 for Triton and Nereid. In this case, we used the WFI catalogue that was generated from observations made with ESO2p2/WFI CCD mosaic that covered the path of Neptune in the sky-plane up to 2016.

In table \ref{Tab: satellite-occultation} it's presented the number of stellar occultations predicted by year for each satellite.

\begin{table}
\caption{\label{Tab: satellite-occultation} Number of stellar occultations for each satellite from 2015 up to 2017}
\begin{centering}
\begin{tabular}{lcccc}
\hline  \hline
%\multicolumn{4}{c}{Diameter of the satellites} \tabularnewline
Satellite  & 2015  & 2016 & 2017 & Total \tabularnewline
\hline
Ananke &  &  & & \tabularnewline
Carme &  &  &  & \tabularnewline
Elara &  &  &  & \tabularnewline
Himalia &  &  &  & \tabularnewline
Lysithea &  &  &  & \tabularnewline
Pasiphae &  & &  & \tabularnewline
Sinope &  &  &  & \tabularnewline
\hdashline
Phoebe & 13 & 22 & 98 & 133\tabularnewline
\hdashline
Nereid & 40 & 11 & 1 & 52 \tabularnewline
Triton &  &  &  & \tabularnewline
\hline
\end{tabular}
\par \end{centering}
\end{table}
